\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts

\begin{document}

%\section{}
%\subsection{}


\centerline{{\bf Basic Project: Stochastic Models for Pacific SST and SSH variability}} 
\vspace{1cm} 

In this project, you will practice with the analysis of observations   and with several 
conceptual stochastic models to explain certain aspects of these data.  Use the Jupyter
notebooks provided on GitHub and make a new Jupyter  notebook for all computations 
below.

\centerline{{\bf Part A, Deadline Report: Friday 7/2 at 13:00}}  

\begin{itemize}
\item[(i)] Read in the two time series of the corresponding data file for this project
(same data set as we used in class). 
The data consists of sea surface height (SSH) and sea surface temperature (SST) 
somewhere in the  Pacific Ocean between 1993 -- 2018.   Plot both the SSH and SST 
anomalies (w.r.t. to the time mean). 

\item[(ii)] Remove the seasonal cycle and long-term trend.   Determine the probability 
density function (PDF) of the time series,  calculate the Fourier spectra and determine 
the power law coefficient of the spectral power decay at high frequency.  Do this for 
both SST and SSH. 

\end{itemize}

\noindent Consider the following stochastic differential equation 
%
\[
dX_t = -\gamma X_t dt + \sigma dW_t 
\]
%
with $X_0$ given and real parameters $\gamma$ and $\sigma$. 

\begin{itemize}

\item[(iii)] Provide a method to estimate the parameters $\gamma$ 
and  $\sigma$  for  both  SSH and SST and  determine their `best' 
values.    

\item[(iv)] For these best estimates, compute a  realization 
of the stochastic model and determine the equilibrium PDF. Compare this 
PDF for the estimated parameters  with the PDF of SSH and 
SST (as in (ii)). Discuss the differences between SST and SSH 
data. 

\end{itemize} 

\newpage 

\centerline{{\bf Part B}}  

Consider next the following stochastic differential equation 
%
\[
dX_t = \lambda X_t dt + (\mu + \nu X_t)  dW_t
\]
%
with $X_0$ given and real parameters $\lambda$, $\mu$
and $\nu$. This stochastic model is called CAM (Correlated  
Additive-Multiplicative) noise. 

\begin{itemize}

\item[(i)]  Determine the analytical equilibrium PDF solution  
of the Fokker-Planck  equation associated with this stochastic 
differential equation. 

\item[(ii)]  Determine the variance  associated with this  
probability density function and plot it as a function 
of $\nu$. 

\item[(iii)] Provide a method to estimate the parameters $\lambda$, 
$\mu$ and $\nu$ for the observations for SST and SSH and  determine 
their values. Give a physical argument why these  parameters are 
different for SST and SSH.  

\item[(iv)] 
Discuss the differences in probability density functions between 
the two different cases  $\nu = 0$ as in part A and $\nu \neq 0$ 
in part B.  

\end{itemize}


\end{document}  